Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-07-26 manuscript/manuscript.tex

As an example, here we look at the fluorescence correlation of Trp-1, since this terminal tryptophan is a realistic experimental observable for our pentapeptide system.
In order to compute the fluorescence correlation functions we require a microscopic, instantaneous value of the tryptophan fluorescence for each of the five macrostates.
%These values are computed using a 'forward model'.
To approximate the fluorescence signal in our pentapeptide system, we use the mdtraj library~\cite{mdtraj} to compute the solvent accessible surface area (SASA) of Trp-1.
Now that we have an approximation of the fluorescence in each of our MSM states, we can use PyEMMA to compute the fluorescence autocorrelation function (ACF) from our MSM (\ref{fig:msm-analysis}e, upper).
Note how the computed ACF has a very small response (i.e., signal amplitude).

>>>>

As an example, here we look at the fluorescence correlation of Trp-1, since this terminal tryptophan is a realistic experimental observable for our pentapeptide system.
In order to compute the fluorescence correlation functions we require a microscopic, instantaneous value of the tryptophan fluorescence for each of the original $75$ MSM microstates.
%These values are computed using a 'forward model'.
To approximate the fluorescence signal in our pentapeptide system, we use the mdtraj library~\cite{mdtraj} to compute the solvent accessible surface area (SASA) of Trp-1.
Now that we have an approximation of the fluorescence in each of our MSM states, we can use PyEMMA to compute the fluorescence autocorrelation function (ACF) from our MSM (\ref{fig:msm-analysis}e, upper).
Note how the computed ACF has a very small response (i.e., signal amplitude).
